MP MetaAnalysis

### 2018-01-25 Analyses.Rmd
update analyses and dataset for time window onset analysis

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
```

@@

```{r TimeWindowOffset}
offset_info <- db_ET_correct %>%
  group_by(offset) %>%
  summarize(count = n())

>>>>

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]

@@

```{r TimeWindowOffset}
offset_info <- time_wind_dat %>%
  group_by(offset) %>%
  summarize(count = n())
